Capacity and Utilization analysis of Toronto shelter(2024)

### 2024-09-26 paper/paper_Li.qmd
Update paper_Li.qmd

#install.packages("tidyverse")
#install.packages("opendatatoronto")
#install.packages("here")
library(tidyverse)
library(opendatatoronto)
library(here)
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

@@

Using the R programming language [@citeR], the `tidyverse` [@thereferencecanbewhatever] package were used to simulate the dataset and generate tests for it. The `opendatatoronto` [@citeopendatatoronto] and `tidyverse` [@thereferencecanbewhatever] packages were then applied in order to download the raw Toronto Public shelter dataset. Next, the `tidyverse` package [@thereferencecanbewhatever] was used to clean the raw dataset and test the cleaned dataset.

@@

#outbreak_cleaned_data <- read_csv(here::here("outputs/data/cleaned_data.csv"))
```

@@

marriage_licence_statistics <- marriage_licence_resources[5,] %>%
  get_resource()
analysis_data = marriage_licence_statistics

@@

# Assuming analysis_data is already loaded and contains the necessary fields
analysis_data$OCCUPANCY_DATE <- as.Date(analysis_data$OCCUPANCY_DATE, format="%Y-%m-%d")

@@

# Plot the occupancy rate trend
ggplot(daily_occupancy_rate, aes(x = OCCUPANCY_DATE)) +
  geom_line(aes(y = Bed_Occupancy_Rate, color = "Bed Occupancy Rate"), size = 1) +
  geom_line(aes(y = Room_Occupancy_Rate, color = "Room Occupancy Rate"), size = 1, linetype = "dashed") +
  labs(title = "", x = "Date", y = "Occupancy Rate (%)") +
  theme_minimal() +
  scale_color_manual(values = c("Bed Occupancy Rate" = "blue", "Room Occupancy Rate" = "red")) +
  theme(legend.title = element_blank())

```
@fig-occupancy-rates shows the occupancy rates for beds and rooms in the shelter system over time. The blue line represents the bed occupancy rate, while the red line represents the room occupancy rate. Overall, the room occupancy rate (red) is higher and more stable, staying close to 100%. In contrast, the bed occupancy rate (blue) shows more fluctuations, generally ranging between 98% and 99%.

@@

# Create a scatter plot using ggplot2
ggplot(scatter_data, aes(x = CAPACITY_ACTUAL_BED, y = OCCUPANCY_RATE_BEDS)) +
  geom_point(alpha = 0.7, size = 1) +  # Set point size to 1 and transparency to 0.7
  labs(title = "", 
       x = "Actual Bed Capacity", 
       y = "Occupancy Rate (Beds)") +
  theme_minimal()  # Use minimal theme
```

>>>>

# install.packages("tidyverse")
# install.packages("opendatatoronto")
# install.packages("here")
library(tidyverse)
library(opendatatoronto)
library(here)
```

@@

@@

The project is structure base on Rohan's principes [@rohan], and used the **R** programming language [@citeR], the `tidyverse` [@thereferencecanbewhatever] package were used to simulate the dataset and generate tests for it. The `opendatatoronto` [@citeopendatatoronto] and `tidyverse` [@thereferencecanbewhatever] packages were then applied in order to download the raw Toronto Public shelter dataset. Next, the `tidyverse` package [@thereferencecanbewhatever] was used to clean the raw dataset and test the cleaned dataset.

@@

# outbreak_cleaned_data <- read_csv(here::here("outputs/data/cleaned_data.csv"))
```

@@

marriage_licence_statistics <- marriage_licence_resources[5, ] %>%
  get_resource()
analysis_data <- marriage_licence_statistics

@@

# Assuming analysis_data is already loaded and contains the necessary fields
analysis_data$OCCUPANCY_DATE <- as.Date(analysis_data$OCCUPANCY_DATE, format = "%Y-%m-%d")

@@

# Plot the occupancy rate trend
ggplot(daily_occupancy_rate, aes(x = OCCUPANCY_DATE)) +
  geom_line(aes(y = Bed_Occupancy_Rate, color = "Bed Occupancy Rate"), size = 1) +
  geom_line(aes(y = Room_Occupancy_Rate, color = "Room Occupancy Rate"), size = 1, linetype = "dashed") +
  labs(title = "", x = "Date", y = "Occupancy Rate (%)") +
  theme_minimal() +
  scale_color_manual(values = c("Bed Occupancy Rate" = "blue", "Room Occupancy Rate" = "red")) +
  theme(legend.title = element_blank())
```
@fig-occupancy-rates shows the occupancy rates for beds and rooms in the shelter system over time. The blue line represents the bed occupancy rate, while the red line represents the room occupancy rate. Overall, the room occupancy rate (red) is higher and more stable, staying close to 100%. In contrast, the bed occupancy rate (blue) shows more fluctuations, generally ranging between 98% and 99%.

@@

# Create a scatter plot using ggplot2
ggplot(scatter_data, aes(x = CAPACITY_ACTUAL_BED, y = OCCUPANCY_RATE_BEDS)) +
  geom_point(alpha = 0.7, size = 1) + # Set point size to 1 and transparency to 0.7
  labs(
    title = "",
    x = "Actual Bed Capacity",
    y = "Occupancy Rate (Beds)"
  ) +
  theme_minimal() # Use minimal theme
```
